Fast and Error-Adaptive Count-Distinct Sketch \\for Influence Maximization

### 2021-01-15 paper.tex
Progress

Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors.
After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
The sketches are assumed as stale if the absolute error in estimated total influence score is more than the global threshold, $\epsilon_{global}$, 
and the marginal gain estimation error after the last sketch is larger than a local threshold $\epsilon_{local}$.

@@

Even though, \acro's behavior is not chaotic with respect to changes in parameters. Our method's performance, both in terms of speed and quality of results, depends on parameter selection. We conducted a grid search over several parameter combinations to illustrate how \acro performs with different parameters. In figure~\ref{fig:parameter-smallmultiples}, both speed and quality of results on some of the largest datasets we have experimented is shown.  We found that, the parameters $\epsilon_{local}=0.3$ and $\epsilon_{global}=0.01$ used in our experiments, performs decent in many datasets, both in terms of speed and quality.

>>>>

Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors.
After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
The sketches are assumed as stale if the absolute error in the estimated total influence score is more than the global threshold, $\epsilon_{global}$, 
and the marginal gain estimation error after the last sketch is larger than a local threshold $\epsilon_{local}$.

@@

Even though, \acro's behavior is not chaotic with respect to changes in parameters. The performance, both in terms of speed and quality of results, depends on parameter selection. We conducted a grid search over several parameter combinations to illustrate how \acro performs with different parameters. In figure~\ref{fig:parameter-smallmultiples}, both the speed and the quality of results on some of the largest datasets we have experimented is shown.  We found that the parameters $\epsilon_{local}=0.3$ and $\epsilon_{global}=0.01$, used in our experiments, performs decent in many datasets, both in terms of speed and quality.
